---
title: "eDNA survey"
author: "Nicole Hack"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: html_document
runtime: shiny 
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F, fig.width = 15.5, fig.height = 9)
```

```{r, include = F}
packages <- c('readxl',
              'tidyverse',
              'readr',
              'data.table',
              'dplyr',
              'car',
              'ggplot2',
              'nortest',
              'broom',
              'lme4',
              'magrittr',
              'forcats',
              'shiny',
              'ggmap',
              'splitstackshape')
lapply(packages, require, character.only = T)
```

```{r}
eDNA <- read_csv("~/eDNA/eDNA questionnaire_pt2.csv")
#rename columns
names(eDNA) = c('Timestamp','email','name','sites','substrate','reference','organism','methods','methref','workgroup','issues')

#separate each site
dat1 = splitstackshape::cSplit(eDNA, 'sites', direction = 'long', drop = F)
dat1$sites = as.character(dat1$sites)
```

```{r Get GPS data}
#need to find gps coordinates of all the sites 
eDNA_gps1 <- read_csv("C:/Users/NHack/Water-board.git/eDNA_gps1.csv")
#add 'california' to geocodes to ensure correct look-up
geo_dat = eDNA_gps1 %>% dplyr::mutate(sites = ifelse(!is.na(sites), paste(sites, 'California'), sites))
#remove duplicates of the word california
geo_dat$sites = gsub('California California', 'California', geo_dat$sites, fixed = T)
#geocode cannot handle NAs so replacing with question marks
geo_dat = geo_dat %>% dplyr::mutate(sites = ifelse(is.na(sites),'?',sites))
geocoded_dat = ggmap::mutate_geocode(geo_dat, sites, override_limit=T)

#times out possibly due to too many searches per second
#particitioning following https://stackoverflow.com/questions/31637181/how-to-parallelelize-do-calls-with-dplyr/33712365#33712365
#library(multidplyr)
#eDNA_gps1$split = 1:3
#test = eDNA_gps1 %>% dplyr::select(sites, split) %>%
  #partition(split)%>% ggmap::mutate_geocode(as.data.frame(test), as.character(test$sites), override_limit=T) %>%
  #collect()

#Confert UTMs to GPS
eDNA_UTMs <- read_excel("~/eDNA/eDNA_UTMs.xlsx")
eDNA_UTMs$Easting<-as.numeric(substr(eDNA_UTMs$Easting,1,nchar(eDNA_UTMs$Easting)-1))
names(eDNA_UTMs)[5] = 'sites'
#split by zone
zone10s = dplyr::filter(eDNA_UTMs, Zone == '10S')
zone10t = dplyr::filter(eDNA_UTMs, Zone == '10T')
#https://stackoverflow.com/questions/30018098/how-to-convert-utm-coordinates-to-lat-and-long-in-r
library(rgdal)
sputm <- SpatialPoints(zone10s[3:4], proj4string=CRS("+proj=utm +zone=10S +datum=WGS84"))  
spgeo <- as.data.frame(spTransform(sputm, CRS("+proj=longlat +datum=WGS84")))
names(spgeo) = c('lon', 'lat')
geo_10s = dplyr::bind_cols(zone10s, spgeo)
#now second zone
sputmt <- SpatialPoints(zone10t[3:4], proj4string=CRS("+proj=utm +zone=10T +datum=WGS84"))  
spgeot <- as.data.frame(spTransform(sputmt, CRS("+proj=longlat +datum=WGS84")))
names(spgeot) = c('lon', 'lat')
geo_10t = dplyr::bind_cols(zone10t, spgeot)
#combine 2 zones
KenRoby_sites = rbind(geo_10s, geo_10t) %>% dplyr::select(name, sites, lat, lon)

#Adding those who supplied proper coordinates
eDNA_coords <- read_excel("C:/Users/NHack/Water-board.git/eDNA_GPS.xlsx")
#Removing location by merging location and site
coord_sites = eDNA_coords %>% dplyr::mutate(sites = ifelse(!is.na(sites),paste(Location, sites, sep = ' '), NA))
#select only relevant columns
coord_sites = dplyr::select(coord_sites, name, sites, lat, lon)

#Combine all datasets together
eDNA_full_coords = rbind(coord_sites, KenRoby_sites, geocoded_dat[-3])
map_coords = dplyr::filter(eDNA_full_coords, !is.na(eDNA_full_coords$lon))
```

##Map of eDNA sample locations in California

```{r Map}
#make shiny map
library(shiny)
library(leaflet)
mapper = function(data) {
  require(shiny)
  require(leaflet)
  shinyApp(
  
  ui = column(width = 12, tags$style(type = "text/css","#map {height: calc(100vh - 90px) !important;}"),
  leafletOutput('map')),
  
  server = function(input,output) {
    output$map <- renderLeaflet({
    leaflet(options = leafletOptions(minZoom = 6)) %>% 
      addProviderTiles(providers$CartoDB.Positron) %>%
      setView(lng = mean(data$lon), 
              lat = mean(data$lat), 
              zoom = 6) %>%
      setMaxBounds(lng1 = -130.3933357,
                   lat1 = 43.108951,
                   lng2 = -109.729128,
                   lat2 = 32.144795)
  })
    observe({
    leafletProxy('map') %>%
      clearShapes() %>%
      addCircles(data = data, #Cannot use addcirclemarkers as popup info does not work
                 lat = ~lat,
                 lng = ~lon,
                 opacity = 1,
                 radius = 5)
    })
  }#closes server
  )#closes shinyApp
}#closes function

ggmap::get_map("California", scale = 2, zoom = 6, maptype = 'roadmap') %>% ggmap()+
  geom_point(data = map_coords, aes(x = lon, y = lat), size = 2)
```

Making graphs of multiple choice data

##Substrate

```{r}
#separate substrate 
dat3 = splitstackshape::cSplit(eDNA, 'substrate', direction = 'long', sep = ';')
#recode
dat4 = dplyr::mutate(dat3, substratesimp = ifelse((dat3$substrate == 'Water' |
                                                    dat3$substrate == 'Soil' |
                                                    dat3$substrate == 'Sediment'),
                     as.character(dat3$substrate), paste('Other')))
ggplot(dat4, aes(fct_infreq(substratesimp)))+
  geom_bar(fill = c('dodgerblue','chocolate4','tan','grey'))+
  xlab('Substrate')+
  ylab('Number of Participants')+
  scale_y_continuous(expand = c(0,0)) +
  theme_classic(base_size = 27)
```

##Please provide detail on your target organisms.

```{r}
#separate substrate 
dat7 = splitstackshape::cSplit(eDNA, 'organism', direction = 'long', sep = ',') %>%
  splitstackshape::cSplit('organism', direction = 'long', sep = ';')
#recode
dat8 = dplyr::mutate(dat7, group = case_when(
  grepl('fish|smelt|trout|sturgeon|salmon|stickleback|steelhead|sculpin|minnow|goby|gill|Myxobolus cerebralis|Eulachon|lamprey|shark|ray', organism, ignore.case = T) ~ 'Fish',
  grepl('frog|toad|salamander|newt|amphibians', organism, ignore.case = T) ~ 'Amphibians',
  grepl('turtle|snake|lizard', organism, ignore.case = T) ~ 'Reptiles',
  grepl('mussel|snail|Anodonta|Margaritifera falcata|Gonidea angulata', organism, ignore.case = T) ~ 'Mollusks',
  grepl('human|mammals|swine|canine|bovine', organism, ignore.case = T) ~ 'Mammals',
  grepl('microorganism|virus*|bacteria|archaea|protists|nova shasta|Bsal|Bd|coliforms|microbe|E. coli|Enterococcus|Bacteroides', organism, ignore.case = T) ~ 'Microorgansims',
  grepl('algae', organism, ignore.case = T) ~ 'Algae',
  grepl('shrimp|crayfish|branchiopods', organism, ignore.case = T) ~ 'Crustaceans',
  grepl('birds|avian', organism, ignore.case = T) ~ 'Birds',
  grepl('plants', organism, ignore.case = T) ~ 'Plants'
))
test = dplyr::select(dat8, organism, group)
#must manually change 'crayfish' from fish to crustacean
dat8[35,'group'] = paste('Crustaceans')

drop_na(dat8, group) %>% ggplot(aes(fct_infreq(group)))+
  geom_bar(fill = c("#56B4E9","darkgreen","#CC79A7", "#0072B2", 'chocolate4', "firebrick","olivedrab","slategrey", "olivedrab2","tan2"))+
  xlab('Organism')+
  ylab('Number of Participants')+
  scale_y_continuous(expand = c(0,0)) +
  theme_classic(base_size = 27)+
  theme(plot.title = element_text(hjust = 0.5),axis.text.x = element_text(angle = 45, hjust = 1))

#make new column of invertebrate/vertebrate/both
dat9 = dat8 %>% dplyr::mutate(vert = case_when(
  grepl('Birds|Mammals|Reptiles|Amphibians|Fish', group) ~ 'Vertebrates',
  grepl('invertebrate', organism, ignore.case = T) ~ 'Invertebrates',
  grepl('Mollusks|Crustaceans',group) ~ 'Invertebrates',
  grepl('vertebrate', organism, ignore.case = T) ~ 'Vertebrates',
  TRUE ~ group
)
)

#want to only have one entry per participant
dat10 = dplyr::select(dat9, -organism, -group)
dat10 = dat10[!duplicated(dat10),]

drop_na(dat10, vert) %>% ggplot(aes(fct_infreq(vert)))+
  geom_bar(fill = c( "#F0E442","#56B4E9","#CC79A7", "olivedrab2","tan2"))+
  xlab('Organism')+
  ylab('Number of Participants')+
  scale_y_continuous(expand = c(0,0)) +
  theme_classic(base_size = 27)
```


##How are you sequencing your eDNA sample? (check all that apply) 

```{r}
#separate methods
dat5 = splitstackshape::cSplit(eDNA, 'methods', direction = 'long', sep = ';')
#recode
dat6 = dplyr::mutate(dat5, methodsimp = ifelse((dat5$methods == 'qPCR' |
                                                    dat5$methods == 'Barcode sequencing' |
                                                    dat5$methods == 'Metabarcode sequencing'),
                     as.character(dat5$methods), paste('Other')))
drop_na(dat6, methodsimp) %>% ggplot(aes(fct_infreq(methodsimp)))+
  geom_bar(fill = c("#000000", "#E69F00", "#56B4E9", "#009E73"))+
  xlab('Method')+
  ylab('Number of Participants')+
  scale_y_continuous(expand = c(0,0)) +
  theme_classic(base_size = 27)
```

##Please provide a published reference or a short description of your sequencing approach.

```{r}
knitr::kable(drop_na(dplyr::select(eDNA, reference, methref)))
```


##Do you believe that there is a need for a statewide eDNA workgroup?

```{r}
ggplot(eDNA, aes(fct_infreq(workgroup)))+
  geom_bar(fill = c("#009E73", "#F0E442", "#D55E00"))+
  xlab('')+
  ylab('Number of Participants')+
  scale_y_continuous(expand = c(0,0)) +
  theme_classic(base_size = 27)
```

##If you answered "yes", what do you believe are the major issues facing the eDNA field today? 

```{r}
knitr::kable(drop_na(dplyr::select(eDNA, issues)))
```

