---
title: "eDNA survey"
author: "Nicole Hack"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
  word_document: default
  html_notenook: default
  pdf_document: default
  html_document: default
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F, fig.width = 15.5, fig.height = 9)
```

```{r, include = F}
packages <- c('readxl',
              'tidyverse',
              'readr',
              'data.table',
              'dplyr',
              'car',
              'ggplot2',
              'nortest',
              'broom',
              'lme4',
              'magrittr',
              'forcats',
              'shiny',
              'ggmap',
              'splitstackshape')
lapply(packages, require, character.only = T)
```

```{r}
eDNA <- read_csv("~/eDNA/eDNA questionnaire_pt2.csv")
#rename columns
names(eDNA) = c('Timestamp','email','name','sites','substrate','reference','organism','methods','methref','workgroup','issues')

#separate each site
dat1 = splitstackshape::cSplit(eDNA, 'sites', direction = 'long', drop = F)
dat1$sites = as.character(dat1$sites)
#need to find gps coordinates of all the sites 
dat2 = ggmap::mutate_geocode(dat1, sites)

```

Making graphs of multiple choice data

##Substrate

```{r}
#separate substrate 
dat3 = splitstackshape::cSplit(eDNA, 'substrate', direction = 'long', sep = ';')
#recode
dat4 = dplyr::mutate(dat3, substratesimp = ifelse((dat3$substrate == 'Water' |
                                                    dat3$substrate == 'Soil' |
                                                    dat3$substrate == 'Sediment'),
                     dat3$substrate, paste('Other')))
ggplot(dat4, aes(fct_infreq(substratesimp)))+
  geom_bar(fill = c('dodgerblue','chocolate4','tan','grey'))+
  xlab('Substrate')+
  ylab('Number of Participants')+
  scale_y_continuous(expand = c(0,0)) +
  theme_classic()
```

##Please provide detail on your target organisms.

```{r}
#separate substrate 
dat7 = splitstackshape::cSplit(eDNA, 'organism', direction = 'long', sep = ',') %>%
  splitstackshape::cSplit('organism', direction = 'long', sep = ';')
#recode
dat8 = dplyr::mutate(dat7, group = case_when(
  grepl('fish|smelt|trout|sturgeon|salmon|stickleback|steelhead|sculpin|minnow|goby|gill|Myxobolus cerebralis|Eulachon|lamprey|shark|ray', organism, ignore.case = T) ~ 'Fish',
  grepl('frog|toad|salamander|newt|amphibians', organism, ignore.case = T) ~ 'Amphibians',
  grepl('turtle|snake|lizard', organism, ignore.case = T) ~ 'Reptiles',
  grepl('mussel|snail|Anodonta|Margaritifera falcata|Gonidea angulata', organism, ignore.case = T) ~ 'Mollusks',
  grepl('human|mammals|swine|canine|bovine', organism, ignore.case = T) ~ 'Mammals',
  grepl('microorganism|virus*|bacteria|archaea|protists|nova shasta|Bsal|Bd|coliforms|microbe|E. coli|Enterococcus|Bacteroides', organism, ignore.case = T) ~ 'Microorgansims',
  grepl('algae', organism, ignore.case = T) ~ 'Algae',
  grepl('shrimp|crayfish|branchiopods', organism, ignore.case = T) ~ 'Crustaceans',
  grepl('birds|avian', organism, ignore.case = T) ~ 'Birds',
  grepl('plants', organism, ignore.case = T) ~ 'Plants'
))
test = dplyr::select(dat8, organism, group)
#must manually change 'crayfish' from fish to crustacean
dat8[35,'group'] = paste('Crustaceans')

drop_na(dat8, group) %>% ggplot(aes(fct_infreq(group)))+
  geom_bar(fill = c("#56B4E9","darkgreen","#CC79A7", "#0072B2", 'chocolate4', "firebrick","olivedrab","slategrey", "olivedrab2","tan2"))+
  xlab('Organism')+
  ylab('Number of Participants')+
  scale_y_continuous(expand = c(0,0)) +
  theme_classic()

#make new column of invertebrate/vertebrate/both
dat9 = dat8 %>% dplyr::mutate(vert = case_when(
  grepl('Birds|Mammals|Reptiles|Amphibians|Fish', group) ~ 'Vertebrates',
  grepl('invertebrate', organism, ignore.case = T) ~ 'Invertebrates',
  grepl('Mollusks|Crustaceans',group) ~ 'Invertebrates',
  grepl('vertebrate', organism, ignore.case = T) ~ 'Vertebrates',
  TRUE ~ group
)
)

#want to only have one entry per participant
dat10 = dplyr::select(dat9, -organism, -group)
dat10 = dat10[!duplicated(dat10),]

drop_na(dat10, vert) %>% ggplot(aes(fct_infreq(vert)))+
  geom_bar(fill = c( "#F0E442","#56B4E9","#CC79A7", "olivedrab2","tan2"))+
  xlab('Organism')+
  ylab('Number of Participants')+
  scale_y_continuous(expand = c(0,0)) +
  theme_classic()
```


##How are you sequencing your eDNA sample? (check all that apply) 

```{r}
#separate methods
dat5 = splitstackshape::cSplit(eDNA, 'methods', direction = 'long', sep = ';')
#recode
dat6 = dplyr::mutate(dat5, methodsimp = ifelse((dat5$methods == 'qPCR' |
                                                    dat5$methods == 'Barcode sequencing' |
                                                    dat5$methods == 'Metabarcode sequencing'),
                     as.character(dat5$methods), paste('Other')))
drop_na(dat6, methodsimp) %>% ggplot(aes(fct_infreq(methodsimp)))+
  geom_bar(fill = c("#000000", "#E69F00", "#56B4E9", "#009E73"))+
  xlab('Method')+
  ylab('Number of Participants')+
  scale_y_continuous(expand = c(0,0)) +
  theme_classic()
```

##Please provide a published reference or a short description of your sequencing approach.

```{r}
knitr::kable(drop_na(dplyr::select(eDNA, reference, methref)))
```


##Do you believe that there is a need for a statewide eDNA workgroup?

```{r}
ggplot(eDNA, aes(fct_infreq(workgroup)))+
  geom_bar(fill = c("#009E73", "#F0E442", "#D55E00"))+
  xlab('')+
  ylab('Number of Participants')+
  scale_y_continuous(expand = c(0,0)) +
  theme_classic()
```

##If you answered "yes", what do you believe are the major issues facing the eDNA field today? 

```{r}
knitr::kable(drop_na(dplyr::select(eDNA, issues)))
```

