---
title: "State Water Board Web and Business Requirements Internal Survey"
author: "Nicole Hack"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
  word_document: default
  html_notenook: default
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F, fig.width = 12, fig.height = 8)
```

```{r, include = F}
packages <- c('readxl',
              'tidyverse',
              'readr',
              'data.table',
              'dplyr',
              'car',
              'ggplot2',
              'nortest',
              'broom',
              'lme4',
              'magrittr',
              'forcats')
lapply(packages, require, character.only = T)
```

```{r}
survey = read_csv("C:/Users/NHack/Water-board.git/Web Team - Internal Survey (Responses) - Form Responses 1.csv")
survey$publishORcollectContent = as.factor(survey$publishORcollectContent)
levels(survey$publishORcollectContent) = c('Collect Content', 'Publish Content', 'Both')
survey = dplyr::mutate(survey, acron = car::recode(division,"
                                                   'Division of Water Rights'= 'DWR';
                                                   'Division of Drinking Water' = 'DDW';
                                                   'Office of Research, Planning & Performance' = 'ORPP';
                                                   'Division of Administrative Services'= 'DAS';
                                                   'Office of the Delta Water Master' = 'ODWM';
                                                   'Division of Financial Assistance' = 'DFA';
                                                   'Office of Information Management & Analysis'= 'OIMA';
                                                   'EEO' = 'EEO';
                                                   'Office of Public Participation' = 'OPP';
                                                   'Division of Water Quality - Surface Water Regulatory Branch' = 'DWQ'"))

#Load division summary to merge with survey data
divison_summary <- read_excel("~/divison_summary.xlsx")
```



Summary of number of programs who participated in this survey.

```{r}
sumsurvey = survey %>% dplyr::group_by(division, acron) %>%
  dplyr::summarise(Participants = n())
#merge 2 datasets
dat1 = left_join(divison_summary, sumsurvey, by = 'acron') %>% 
  dplyr::mutate(PercentParticipation = ceiling((Participants / NumStaff) * 100)) %>% 
  dplyr::select(-division)

sumstaff = survey %>% dplyr::group_by(acron) %>% dplyr::summarise(staffnum = sum(ceiling(Staffnum)),webhrs = sum(ceiling(hoursnum)))
sumstaff$acron = reorder(sumstaff$acron, sumstaff$staffnum)
dat2 = left_join(dat1, sumstaff, by ='acron') %>% mutate(percap = round(webhrs / staffnum, digits = 2))

knitr::kable(dat1)

ggplot(survey, aes(x = reorder(acron,Rank), fill = as.factor(Rank)))+
  geom_bar()+
  xlab('')+
  scale_fill_discrete(labels = c('CEAs', 'Program Managers', 'Senior Managers', 'else'))+
  scale_y_continuous(expand = c(0,0)) +
  theme_classic(base_size=20)+
  ylab('Count')+
  theme(legend.title = element_blank())

#Ranks for participant titles
# 1 = CEAs
# 2 = Assistant Deputy Director, Program manageer, Staff Service Manager (II & III), Supervising Engineers
# 3 = Staff service manager I, Senior Enviornmental Scientists, Senior Engineers
# 4 = Environmental Scientists, Engineering Geologist, Specialists
```


##In your program(s), do you use use the web site to publish content, collect content, or both?

```{r}
websiteuse = survey %>% dplyr::group_by(acron) %>% count(publishORcollectContent)
ggplot(websiteuse, aes(x = publishORcollectContent, y = n, fill = acron))+
  geom_bar(stat = 'identity')+
  xlab('')+
  scale_y_continuous(expand = c(0,0)) +
  theme_classic(base_size=20)+
  ylab('Number of Programs')+
  theme(legend.title = element_blank())
ggsave(filename = 'testplot.jpg')
```

##Identify the types and locations of content posted by your program(s). 

```{r}
locations = dplyr::select(survey,name,division, acron,programs,contains('Location'))
locationsbyweb = tidyr::gather(locations, 'Document','Location',5:length(locations))
locationsbyweb$Document = gsub('Location','',locationsbyweb$Document)
levels(locationsbyweb$Location) = c('Both','State Water Board Home Page','Program Home and Sub-Page(s)','N/A')
ggplot(locationsbyweb, aes(x = acron, fill = factor(Location, levels = c('Both','State Water Board Home Page','Program Home and Sub-Page(s)','N/A'))))+
  geom_bar()+
  ylab('Number of Programs')+
  guides(fill = guide_legend(title = 'Web Page'))+
  coord_flip()+
  scale_fill_manual(values = c('darkturquoise','Blue','forestgreen','Grey'))+
  scale_y_continuous(expand = c(0,0)) +
  theme_classic(base_size=20)+
  theme(axis.title.y = element_blank())
```



```{r}
ggplot(locationsbyweb, aes(x = Document, fill = factor(Location, levels = c('Both','State Water Board Home Page','Program Home and Sub-Page(s)','N/A'))))+
  geom_bar()+
  ylab('Number of Programs')+
  guides(fill = guide_legend(title = 'Web Page'))+
  coord_flip()+
  scale_fill_manual(values = c('darkturquoise','Blue','forestgreen','Grey'))+
  scale_y_continuous(expand = c(0,0)) +
  theme_classic(base_size=20)+
  theme(axis.title.y = element_blank())
```

##What are the most applicable core business use categories for the web page(s) used by your program(s)?

```{r}
library(splitstackshape)
surveyFunction = cSplit(survey,'Function', ',') %>%
  tidyr::gather('FunNum','MainCat',28:length(.)) %>%
  dplyr::select('name', 'division', 'acron','programs', 'MainCat')
surveyFunction$MainCat = car::recode(surveyFunction$MainCat,"'Announcements' = 'Annoucements';
              'Public Record (Orders' = 'Public Records';
              'Coordination/Organizational Use (Agendas' = 'Coordination/Organizational Use';
              'Achievements/ Work Products' = 'Achievements/ Work Products';
              'Education & Training' = 'Education & Training';
              'Outreach' = 'Outreach';
              'Program Overview/Information' = 'Program Overview/Information';
              'Repository/Library/Collection (of internally and externally developed resources and links)' = 'Repository';
              else = NA")
surveyFunction = surveyFunction[complete.cases(surveyFunction),]

ggplot(surveyFunction, aes(fill = acron, x = fct_infreq(MainCat)))+
  geom_bar()+
  ylab('Number of Programs')+
  guides(fill = guide_legend(title = ''))+
  coord_flip()+
  scale_y_continuous(expand = c(0,0)) +
  theme_classic(base_size=20)+
  theme(axis.title.y = element_blank(),plot.margin=unit(c(1,1,1.5,1.2),"cm"))
```

##Who are the target audiences for the web pages used by your program?

```{r}
audience = survey %>% cSplit('audience', ',') %>%
  tidyr::gather('Trash','Audience',28:length(.)) %>%
  dplyr::select('name', 'division','acron', 'programs', 'Audience')
audience$Audience = car::recode(audience$Audience,"
'Internal Staff' = 'Internal Staff';
'Private Industry (Ag' = 'Private Industry';
'Non-Government Organizations (NGOs)' = 'Non-Government Organizations (NGOs)';
'General Public' = 'General Public';
'Businesses' = 'Businesses';
'Municipalities' = 'Municipalities';
'Management' = 'Management';
'Other Agencies' = 'Other Agencies';
'Tribes' = 'Tribes';
'Citizen Scientists' = 'Citizen Scientists';
'Certified operators' = 'Certified operators';
'Retail and wholesale water suppliers throughout the state with an emphasis on 410 urban water suppliers.' = 'Water suppliers';
else = NA")
audience = audience[complete.cases(audience),]

ggplot(audience, aes(fill = acron, x = fct_infreq(Audience)))+
  geom_bar()+
  ylab('Number of Programs')+
  guides(fill = guide_legend(title = ''))+
  coord_flip()+
  scale_y_continuous(expand = c(0,0)) +
  theme_classic(base_size=20)+
  theme(axis.title.y = element_blank(),plot.margin=unit(c(1,1,1.5,1.2),"cm"))
```

##Identify the number of staff utilized to keep content relevant and current. 

```{r}
ggplot(sumstaff, aes(x = acron, y = staffnum))+
  geom_bar(stat = 'identity', color = 'black', fill = 'Blue')+
  ylab('Number of staff')+
  xlab('Divisions & Offices')+
  guides(fill = guide_legend(title = ''))+
  scale_y_continuous(expand = c(0,0)) +
  theme_classic(base_size=20)+
  theme(plot.margin=unit(c(1,1,1.5,1.2),"cm"))
```

##Identify the approximate amount of hours expended each month to keep content relevant and current.

```{r}
ggplot(sumstaff, aes(x = reorder(acron, webhrs), y = webhrs))+
  geom_bar(stat = 'identity', color = 'black', fill = 'Blue')+
  ylab('Number of hr/mo')+
  xlab('Divisions & Offices')+
  guides(fill = guide_legend(title = ''))+
  scale_y_continuous(expand = c(0,0)) +
  theme_classic(base_size=20)+
  theme(plot.margin=unit(c(1,1,1.5,1.2),"cm"))

ggplot(sumstaff, aes(x = staffnum, y = webhrs, color = acron))+
  geom_point(size = 3)+
  xlab('Number of Staff')+
  ylab('Number of hr/mo')+
  guides(color = guide_legend(title = ''))+
  theme_classic(base_size=20)+
  theme(plot.margin=unit(c(1,1,1.5,1.2),"cm"))

ggplot(dat2[complete.cases(dat2),], aes(x = reorder(acron, percap), y = percap))+
  geom_bar(stat = 'identity', color = 'black', fill = 'Blue')+
  ylab('Per Capita Work (hr/p)')+
  xlab('Divisions & Offices')+
  guides(fill = guide_legend(title = ''))+
  scale_y_continuous(expand = c(0,0)) +
  theme_classic(base_size=20)+
  theme(plot.margin=unit(c(1,1,1.5,1.2),"cm"))
```



##How frequently is content updated from your program(s)?

```{r}
survey$ContentUpdate = factor(survey$ContentUpdate, levels = c('Yearly','Quarterly','Monthly','Weekly','Daily','Hourly'))
ggplot(survey, aes(x = sort(ContentUpdate), fill = acron))+
  geom_bar()+
  ylab('Number of programs')+
  xlab('Divisions & Offices')+
  guides(fill = guide_legend(title = ''))+
  scale_y_continuous(expand = c(0,0)) +
  theme_classic(base_size=20)+
  theme(plot.margin=unit(c(1,1,1.5,1.2),"cm"))
```

----

#DAS

```{r}
splitsurvey = split(survey, survey$acron) 
surveynames = unique(survey$acron)
DAS = as.data.frame(splitsurvey[1])
```


##In your program(s), do you use use the web site to publish content, collect content, or both?

```{r}
ggplot(DAS, aes(x = DAS.publishORcollectContent))+
  geom_bar(fill = '#F97564')+
  xlab('')+
  scale_y_continuous(expand = c(0,0)) +
  theme_classic(base_size=20)+
  ylab('Number of Participants')+
  theme(legend.title = element_blank())
```

##Identify the types and locations of content posted by your program(s). 

```{r}
ggplot(filter(locationsbyweb, acron == 'DAS'), aes(x = factor(Location, levels = c('Both','State Water Board Home Page','Program Home and Sub-Page(s)','N/A'))))+
  geom_bar(fill = '#F97564')+
  ylab('Number of Programs')+
  guides(fill = guide_legend(title = 'Web Page'))+
  coord_flip()+
  scale_fill_manual(values = c('darkturquoise','Blue','forestgreen','Grey'))+
  scale_y_continuous(expand = c(0,0)) +
  theme_classic(base_size=20)+
  theme(axis.title.y = element_blank())
```



```{r}
ggplot(filter(locationsbyweb, acron == 'DAS'), aes(x = Document, fill = factor(Location, levels = c('Both','State Water Board Home Page','Program Home and Sub-Page(s)','N/A'))))+
  geom_bar()+
  ylab('Number of Participants')+
  guides(fill = guide_legend(title = 'Web Page'))+
  coord_flip()+
  scale_fill_manual(values = c('darkturquoise','Blue','forestgreen','Grey'))+
  scale_y_continuous(expand = c(0,0)) +
  theme_classic(base_size=20)+
  theme(axis.title.y = element_blank())
```

##What are the most applicable core business use categories for the web page(s) used by your program(s)?

```{r}
ggplot(dplyr::filter(surveyFunction, acron == 'DAS'), aes(x = fct_infreq(MainCat)))+
  geom_bar(fill = '#F97564')+
  ylab('Count')+
  guides(fill = guide_legend(title = ''))+
  coord_flip()+
  scale_y_continuous(expand = c(0,0)) +
  theme_classic(base_size=20)+
  theme(axis.title.y = element_blank(),plot.margin=unit(c(1,1,1.5,1.2),"cm"))
```

##Who are the target audiences for the web pages used by your program?

```{r}
ggplot(dplyr::filter(audience, acron == 'DAS'), aes(x = fct_infreq(Audience)))+
  geom_bar(fill = '#F97564')+
  ylab('Count')+
  guides(fill = guide_legend(title = ''))+
  coord_flip()+
  scale_y_continuous(expand = c(0,0)) +
  theme_classic(base_size=20)+
  theme(axis.title.y = element_blank(),plot.margin=unit(c(1,1,1.5,1.2),"cm"))
```

##How frequently is content updated from your program(s)?

```{r}
ggplot(dplyr::filter(survey, acron == 'DAS'), aes(x = sort(ContentUpdate)))+
  geom_bar(fill = '#F97564')+
  ylab('Count')+
  xlab('Divisions & Offices')+
  guides(fill = guide_legend(title = ''))+
  scale_y_continuous(expand = c(0,0)) +
  theme_classic(base_size=20)+
  theme(plot.margin=unit(c(1,1,1.5,1.2),"cm"))
```

##Participants

```{r}
DASex = dplyr::filter(survey, acron == 'DAS') %>% dplyr::select(name, programs, WebsiteCreation, ContentTools, website, WebsiteExplanation)
knitr::kable(DASex[1])
```

##Describe, in general terms, the process by which your program web pages are developed, updated, and approved for submission to the DIT Web Unit.

```{r}
knitr::kable(DASex$WebsiteCreation)
```

##Describe, in general terms, any processes or tools utilized to keep content relevant and current.

```{r}
knitr::kable(DASex[4])
```

##Provide a web address of a page from your program that you feel best demonstrates your program’s ability to use the web to meet your business requirements.

```{r}
knitr::kable(DASex[5])
```

##Briefly tell us why you selected that web page.
 
```{r}
knitr::kable(DASex[6])
```


----

#DDW

```{r}
DDW = as.data.frame(splitsurvey[2])
```


##In your program(s), do you use use the web site to publish content, collect content, or both?

```{r}
ggplot(DDW, aes(x = DDW.publishORcollectContent))+
  geom_bar(fill = '#DA8E02')+
  xlab('')+
  scale_y_continuous(expand = c(0,0)) +
  theme_classic(base_size=20)+
  ylab('Number of Participants')+
  theme(legend.title = element_blank())
```

##Identify the types and locations of content posted by your program(s). 

```{r}
ggplot(filter(locationsbyweb, acron == 'DDW'), aes(x = factor(Location, levels = c('Both','State Water Board Home Page','Program Home and Sub-Page(s)','N/A'))))+
  geom_bar(fill = '#DA8E02')+
  ylab('Number of Programs')+
  guides(fill = guide_legend(title = 'Web Page'))+
  coord_flip()+
  scale_fill_manual(values = c('darkturquoise','Blue','forestgreen','Grey'))+
  scale_y_continuous(expand = c(0,0)) +
  theme_classic(base_size=20)+
  theme(axis.title.y = element_blank())
```



```{r}
ggplot(filter(locationsbyweb, acron == 'DDW'), aes(x = Document, fill = factor(Location, levels = c('Both','State Water Board Home Page','Program Home and Sub-Page(s)','N/A'))))+
  geom_bar()+
  ylab('Number of Participants')+
  guides(fill = guide_legend(title = 'Web Page'))+
  coord_flip()+
  scale_fill_manual(values = c('darkturquoise','Blue','forestgreen','Grey'))+
  scale_y_continuous(expand = c(0,0)) +
  theme_classic(base_size=20)+
  theme(axis.title.y = element_blank())
```

##What are the most applicable core business use categories for the web page(s) used by your program(s)?

```{r}
ggplot(dplyr::filter(surveyFunction, acron == 'DDW'), aes(x = fct_infreq(MainCat)))+
  geom_bar(fill = '#DA8E02')+
  ylab('Count')+
  guides(fill = guide_legend(title = ''))+
  coord_flip()+
  scale_y_continuous(expand = c(0,0)) +
  theme_classic(base_size=20)+
  theme(axis.title.y = element_blank(),plot.margin=unit(c(1,1,1.5,1.2),"cm"))
```

##Who are the target audiences for the web pages used by your program?

```{r}
ggplot(dplyr::filter(audience, acron == 'DDW'), aes(x = fct_infreq(Audience)))+
  geom_bar(fill = '#DA8E02')+
  ylab('Count')+
  guides(fill = guide_legend(title = ''))+
  coord_flip()+
  scale_y_continuous(expand = c(0,0)) +
  theme_classic(base_size=20)+
  theme(axis.title.y = element_blank(),plot.margin=unit(c(1,1,1.5,1.2),"cm"))
```

##How frequently is content updated from your program(s)?

```{r}
ggplot(dplyr::filter(survey, acron == 'DDW'), aes(x = sort(ContentUpdate)))+
  geom_bar(fill = '#DA8E02')+
  ylab('Count')+
  xlab('Divisions & Offices')+
  guides(fill = guide_legend(title = ''))+
  scale_y_continuous(expand = c(0,0)) +
  theme_classic(base_size=20)+
  theme(plot.margin=unit(c(1,1,1.5,1.2),"cm"))
```


##Participants

```{r}
DDWex = dplyr::filter(survey, acron == 'DDW') %>% dplyr::select(name, programs, WebsiteCreation, ContentTools, website, WebsiteExplanation)
knitr::kable(DDWex[1])
```

##Describe, in general terms, the process by which your program web pages are developed, updated, and approved for submission to the DIT Web Unit.

```{r}
knitr::kable(DDWex$WebsiteCreation)
```

##Describe, in general terms, any processes or tools utilized to keep content relevant and current.

```{r}
knitr::kable(DDWex[4])
```

##Provide a web address of a page from your program that you feel best demonstrates your program’s ability to use the web to meet your business requirements.

```{r}
knitr::kable(DDWex[5])
```

##Briefly tell us why you selected that web page.
 
```{r}
knitr::kable(DDWex[6])
```


----

#DFA

```{r}
DFA = as.data.frame(splitsurvey[3])
```


##In your program(s), do you use use the web site to publish content, collect content, or both?

```{r}
ggplot(DFA, aes(x = DFA.publishORcollectContent))+
  geom_bar(fill = '#A4A408')+
  xlab('')+
  scale_y_continuous(expand = c(0,0)) +
  theme_classic(base_size=20)+
  ylab('Number of Participants')+
  theme(legend.title = element_blank())
```

##Identify the types and locations of content posted by your program(s). 

```{r}
ggplot(filter(locationsbyweb, acron == 'DFA'), aes(x = factor(Location, levels = c('Both','State Water Board Home Page','Program Home and Sub-Page(s)','N/A'))))+
  geom_bar(fill = '#A4A408')+
  ylab('Number of Programs')+
  guides(fill = guide_legend(title = 'Web Page'))+
  coord_flip()+
  scale_fill_manual(values = c('darkturquoise','Blue','forestgreen','Grey'))+
  scale_y_continuous(expand = c(0,0)) +
  theme_classic(base_size=20)+
  theme(axis.title.y = element_blank())
```



```{r}
ggplot(filter(locationsbyweb, acron == 'DFA'), aes(x = Document, fill = factor(Location, levels = c('Both','State Water Board Home Page','Program Home and Sub-Page(s)','N/A'))))+
  geom_bar()+
  ylab('Number of Participants')+
  guides(fill = guide_legend(title = 'Web Page'))+
  coord_flip()+
  scale_fill_manual(values = c('darkturquoise','Blue','forestgreen','Grey'))+
  scale_y_continuous(expand = c(0,0)) +
  theme_classic(base_size=20)+
  theme(axis.title.y = element_blank())
```

##What are the most applicable core business use categories for the web page(s) used by your program(s)?

```{r}
ggplot(dplyr::filter(surveyFunction, acron == 'DFA'), aes(x = fct_infreq(MainCat)))+
  geom_bar(fill = '#A4A408')+
  ylab('Count')+
  guides(fill = guide_legend(title = ''))+
  coord_flip()+
  scale_y_continuous(expand = c(0,0)) +
  theme_classic(base_size=20)+
  theme(axis.title.y = element_blank(),plot.margin=unit(c(1,1,1.5,1.2),"cm"))
```

##Who are the target audiences for the web pages used by your program?

```{r}
ggplot(dplyr::filter(audience, acron == 'DFA'), aes(x = fct_infreq(Audience)))+
  geom_bar(fill = '#A4A408')+
  ylab('Count')+
  guides(fill = guide_legend(title = ''))+
  coord_flip()+
  scale_y_continuous(expand = c(0,0)) +
  theme_classic(base_size=20)+
  theme(axis.title.y = element_blank(),plot.margin=unit(c(1,1,1.5,1.2),"cm"))
```

##How frequently is content updated from your program(s)?

```{r}
ggplot(dplyr::filter(survey, acron == 'DFA'), aes(x = sort(ContentUpdate)))+
  geom_bar(fill = '#A4A408')+
  ylab('Count')+
  xlab('Divisions & Offices')+
  guides(fill = guide_legend(title = ''))+
  scale_y_continuous(expand = c(0,0)) +
  theme_classic(base_size=20)+
  theme(plot.margin=unit(c(1,1,1.5,1.2),"cm"))
```

##Participants

```{r}
DFAex = dplyr::filter(survey, acron == 'DFA') %>% dplyr::select(name, programs, WebsiteCreation, ContentTools, website, WebsiteExplanation)
knitr::kable(DFAex[1])
```

##Describe, in general terms, the process by which your program web pages are developed, updated, and approved for submission to the DIT Web Unit.

```{r}
knitr::kable(DFAex$WebsiteCreation)
```

##Describe, in general terms, any processes or tools utilized to keep content relevant and current.

```{r}
knitr::kable(DFAex[4])
```

##Provide a web address of a page from your program that you feel best demonstrates your program’s ability to use the web to meet your business requirements.

```{r}
knitr::kable(DFAex[5])
```

##Briefly tell us why you selected that web page.
 
```{r}
knitr::kable(DFAex[6])
```



----

#DWQ

```{r}
DWQ = as.data.frame(splitsurvey[4])
```


##In your program(s), do you use use the web site to publish content, collect content, or both?

```{r}
ggplot(DWQ, aes(x = DWQ.publishORcollectContent))+
  geom_bar(fill = '#3CB602')+
  xlab('')+
  scale_y_continuous(expand = c(0,0)) +
  theme_classic(base_size=20)+
  ylab('Number of Participants')+
  theme(legend.title = element_blank())
```

##Identify the types and locations of content posted by your program(s). 

```{r}
ggplot(filter(locationsbyweb, acron == 'DWQ'), aes(x = factor(Location, levels = c('Both','State Water Board Home Page','Program Home and Sub-Page(s)','N/A'))))+
  geom_bar(fill = '#3CB602')+
  ylab('Number of Programs')+
  guides(fill = guide_legend(title = 'Web Page'))+
  coord_flip()+
  scale_fill_manual(values = c('darkturquoise','Blue','forestgreen','Grey'))+
  scale_y_continuous(expand = c(0,0)) +
  theme_classic(base_size=20)+
  theme(axis.title.y = element_blank())
```



```{r}
ggplot(filter(locationsbyweb, acron == 'DWQ'), aes(x = Document, fill = factor(Location, levels = c('Both','State Water Board Home Page','Program Home and Sub-Page(s)','N/A'))))+
  geom_bar()+
  ylab('Number of Participants')+
  guides(fill = guide_legend(title = 'Web Page'))+
  coord_flip()+
  scale_fill_manual(values = c('darkturquoise','Blue','forestgreen','Grey'))+
  scale_y_continuous(expand = c(0,0)) +
  theme_classic(base_size=20)+
  theme(axis.title.y = element_blank())
```

##What are the most applicable core business use categories for the web page(s) used by your program(s)?

```{r}
ggplot(dplyr::filter(surveyFunction, acron == 'DWQ'), aes(x = fct_infreq(MainCat)))+
  geom_bar(fill = '#3CB602')+
  ylab('Count')+
  guides(fill = guide_legend(title = ''))+
  coord_flip()+
  scale_y_continuous(expand = c(0,0)) +
  theme_classic(base_size=20)+
  theme(axis.title.y = element_blank(),plot.margin=unit(c(1,1,1.5,1.2),"cm"))
```

##Who are the target audiences for the web pages used by your program?

```{r}
ggplot(dplyr::filter(audience, acron == 'DWQ'), aes(x = fct_infreq(Audience)))+
  geom_bar(fill = '#3CB602')+
  ylab('Count')+
  guides(fill = guide_legend(title = ''))+
  coord_flip()+
  scale_y_continuous(expand = c(0,0)) +
  theme_classic(base_size=20)+
  theme(axis.title.y = element_blank(),plot.margin=unit(c(1,1,1.5,1.2),"cm"))
```

##How frequently is content updated from your program(s)?

```{r}
ggplot(dplyr::filter(survey, acron == 'DWQ'), aes(x = sort(ContentUpdate)))+
  geom_bar(fill = '#3CB602')+
  ylab('Count')+
  xlab('Divisions & Offices')+
  guides(fill = guide_legend(title = ''))+
  scale_y_continuous(expand = c(0,0)) +
  theme_classic(base_size=20)+
  theme(plot.margin=unit(c(1,1,1.5,1.2),"cm"))
```


##Participants

```{r}
DWQex = dplyr::filter(survey, acron == 'DWQ') %>% dplyr::select(name, programs, WebsiteCreation, ContentTools, website, WebsiteExplanation)
knitr::kable(DWQex[1])
```

##Describe, in general terms, the process by which your program web pages are developed, updated, and approved for submission to the DIT Web Unit.

```{r}
knitr::kable(DWQex$WebsiteCreation)
```

##Describe, in general terms, any processes or tools utilized to keep content relevant and current.

```{r}
knitr::kable(DWQex[4])
```

##Provide a web address of a page from your program that you feel best demonstrates your program’s ability to use the web to meet your business requirements.

```{r}
knitr::kable(DWQex[5])
```

##Briefly tell us why you selected that web page.
 
```{r}
knitr::kable(DWQex[6])
```


----

#DWR

```{r}
DWR = as.data.frame(splitsurvey[5])
```


##In your program(s), do you use use the web site to publish content, collect content, or both?

```{r}
ggplot(DWR, aes(x = DWR.publishORcollectContent))+
  geom_bar(fill = '#01C177')+
  xlab('')+
  scale_y_continuous(expand = c(0,0)) +
  theme_classic(base_size=20)+
  ylab('Number of Participants')+
  theme(legend.title = element_blank())
```

##Identify the types and locations of content posted by your program(s). 

```{r}
ggplot(filter(locationsbyweb, acron == 'DWR'), aes(x = factor(Location, levels = c('Both','State Water Board Home Page','Program Home and Sub-Page(s)','N/A'))))+
  geom_bar(fill = '#01C177')+
  ylab('Number of Programs')+
  guides(fill = guide_legend(title = 'Web Page'))+
  coord_flip()+
  scale_fill_manual(values = c('darkturquoise','Blue','forestgreen','Grey'))+
  scale_y_continuous(expand = c(0,0)) +
  theme_classic(base_size=20)+
  theme(axis.title.y = element_blank())
```



```{r}
ggplot(filter(locationsbyweb, acron == 'DWR'), aes(x = Document, fill = factor(Location, levels = c('Both','State Water Board Home Page','Program Home and Sub-Page(s)','N/A'))))+
  geom_bar()+
  ylab('Number of Participants')+
  guides(fill = guide_legend(title = 'Web Page'))+
  coord_flip()+
  scale_fill_manual(values = c('darkturquoise','Blue','forestgreen','Grey'))+
  scale_y_continuous(expand = c(0,0)) +
  theme_classic(base_size=20)+
  theme(axis.title.y = element_blank())
```

##What are the most applicable core business use categories for the web page(s) used by your program(s)?

```{r}
ggplot(dplyr::filter(surveyFunction, acron == 'DWR'), aes(x = fct_infreq(MainCat)))+
  geom_bar(fill = '#01C177')+
  ylab('Count')+
  guides(fill = guide_legend(title = ''))+
  coord_flip()+
  scale_y_continuous(expand = c(0,0)) +
  theme_classic(base_size=20)+
  theme(axis.title.y = element_blank(),plot.margin=unit(c(1,1,1.5,1.2),"cm"))
```

##Who are the target audiences for the web pages used by your program?

```{r}
ggplot(dplyr::filter(audience, acron == 'DWR'), aes(x = fct_infreq(Audience)))+
  geom_bar(fill = '#01C177')+
  ylab('Count')+
  guides(fill = guide_legend(title = ''))+
  coord_flip()+
  scale_y_continuous(expand = c(0,0)) +
  theme_classic(base_size=20)+
  theme(axis.title.y = element_blank(),plot.margin=unit(c(1,1,1.5,1.2),"cm"))
```

##How frequently is content updated from your program(s)?

```{r}
ggplot(dplyr::filter(survey, acron == 'DWR'), aes(x = sort(ContentUpdate)))+
  geom_bar(fill = '#01C177')+
  ylab('Count')+
  xlab('Divisions & Offices')+
  guides(fill = guide_legend(title = ''))+
  scale_y_continuous(expand = c(0,0)) +
  theme_classic(base_size=20)+
  theme(plot.margin=unit(c(1,1,1.5,1.2),"cm"))
```


##Participants

```{r}
DWRex = dplyr::filter(survey, acron == 'DWR') %>% dplyr::select(name, programs, WebsiteCreation, ContentTools, website, WebsiteExplanation)
knitr::kable(OIMAex[1])
```

##Describe, in general terms, the process by which your program web pages are developed, updated, and approved for submission to the DIT Web Unit.

```{r}
knitr::kable(DWRex$WebsiteCreation)
```

##Describe, in general terms, any processes or tools utilized to keep content relevant and current.

```{r}
knitr::kable(DWRex[4])
```

##Provide a web address of a page from your program that you feel best demonstrates your program’s ability to use the web to meet your business requirements.

```{r}
knitr::kable(DWRex[5])
```

##Briefly tell us why you selected that web page.
 
```{r}
knitr::kable(DWRex[6])
```



----

#EEO

```{r}
EEO = as.data.frame(splitsurvey[6])
```


##In your program(s), do you use use the web site to publish content, collect content, or both?

```{r}
ggplot(EEO, aes(x = EEO.publishORcollectContent))+
  geom_bar(fill = '#06BBBF')+
  xlab('')+
  scale_y_continuous(expand = c(0,0)) +
  theme_classic(base_size=20)+
  ylab('Number of Participants')+
  theme(legend.title = element_blank())
```

##Identify the types and locations of content posted by your program(s). 

```{r}
ggplot(filter(locationsbyweb, acron == 'EEO'), aes(x = factor(Location, levels = c('Both','State Water Board Home Page','Program Home and Sub-Page(s)','N/A'))))+
  geom_bar(fill = '#06BBBF')+
  ylab('Number of Programs')+
  guides(fill = guide_legend(title = 'Web Page'))+
  coord_flip()+
  scale_fill_manual(values = c('darkturquoise','Blue','forestgreen','Grey'))+
  scale_y_continuous(expand = c(0,0)) +
  theme_classic(base_size=20)+
  theme(axis.title.y = element_blank())
```



```{r}
ggplot(filter(locationsbyweb, acron == 'EEO'), aes(x = Document, fill = factor(Location, levels = c('Both','State Water Board Home Page','Program Home and Sub-Page(s)','N/A'))))+
  geom_bar()+
  ylab('Number of Participants')+
  guides(fill = guide_legend(title = 'Web Page'))+
  coord_flip()+
  scale_fill_manual(values = c('darkturquoise','Blue','forestgreen','Grey'))+
  scale_y_continuous(expand = c(0,0)) +
  theme_classic(base_size=20)+
  theme(axis.title.y = element_blank())
```

##What are the most applicable core business use categories for the web page(s) used by your program(s)?

```{r}
ggplot(dplyr::filter(surveyFunction, acron == 'EEO'), aes(x = fct_infreq(MainCat)))+
  geom_bar(fill = '#06BBBF')+
  ylab('Count')+
  guides(fill = guide_legend(title = ''))+
  coord_flip()+
  scale_y_continuous(expand = c(0,0)) +
  theme_classic(base_size=20)+
  theme(axis.title.y = element_blank(),plot.margin=unit(c(1,1,1.5,1.2),"cm"))
```

##Who are the target audiences for the web pages used by your program?

```{r}
ggplot(dplyr::filter(audience, acron == 'EEO'), aes(x = fct_infreq(Audience)))+
  geom_bar(fill = '#06BBBF')+
  ylab('Count')+
  guides(fill = guide_legend(title = ''))+
  coord_flip()+
  scale_y_continuous(expand = c(0,0)) +
  theme_classic(base_size=20)+
  theme(axis.title.y = element_blank(),plot.margin=unit(c(1,1,1.5,1.2),"cm"))
```

##How frequently is content updated from your program(s)?

```{r}
ggplot(dplyr::filter(survey, acron == 'EEO'), aes(x = sort(ContentUpdate)))+
  geom_bar(fill = '#06BBBF')+
  ylab('Count')+
  xlab('Divisions & Offices')+
  guides(fill = guide_legend(title = ''))+
  scale_y_continuous(expand = c(0,0)) +
  theme_classic(base_size=20)+
  theme(plot.margin=unit(c(1,1,1.5,1.2),"cm"))
```


##Participants

```{r}
EEOex = dplyr::filter(survey, acron == 'EEO') %>% dplyr::select(name, programs, WebsiteCreation, ContentTools, website, WebsiteExplanation)
knitr::kable(OIMAex[1])
```

##Describe, in general terms, the process by which your program web pages are developed, updated, and approved for submission to the DIT Web Unit.

```{r}
knitr::kable(EEOex$WebsiteCreation)
```

##Describe, in general terms, any processes or tools utilized to keep content relevant and current.

```{r}
knitr::kable(EEOex[4])
```

##Provide a web address of a page from your program that you feel best demonstrates your program’s ability to use the web to meet your business requirements.

```{r}
knitr::kable(EEOex[5])
```

##Briefly tell us why you selected that web page.
 
```{r}
knitr::kable(EEOex[6])
```



----

#ODWM

```{r}
ODWM = as.data.frame(splitsurvey[7])
```


##In your program(s), do you use use the web site to publish content, collect content, or both?

```{r}
ggplot(ODWM, aes(x = ODWM.publishORcollectContent))+
  geom_bar(fill = '#00B1F9')+
  xlab('')+
  scale_y_continuous(expand = c(0,0)) +
  theme_classic(base_size=20)+
  ylab('Number of Participants')+
  theme(legend.title = element_blank())
```

##Identify the types and locations of content posted by your program(s). 

```{r}
ggplot(filter(locationsbyweb, acron == 'ODWM'), aes(x = factor(Location, levels = c('Both','State Water Board Home Page','Program Home and Sub-Page(s)','N/A'))))+
  geom_bar(fill = '#00B1F9')+
  ylab('Number of Programs')+
  guides(fill = guide_legend(title = 'Web Page'))+
  coord_flip()+
  scale_fill_manual(values = c('darkturquoise','Blue','forestgreen','Grey'))+
  scale_y_continuous(expand = c(0,0)) +
  theme_classic(base_size=20)+
  theme(axis.title.y = element_blank())
```



```{r}
ggplot(filter(locationsbyweb, acron == 'ODWM'), aes(x = Document, fill = factor(Location, levels = c('Both','State Water Board Home Page','Program Home and Sub-Page(s)','N/A'))))+
  geom_bar()+
  ylab('Number of Participants')+
  guides(fill = guide_legend(title = 'Web Page'))+
  coord_flip()+
  scale_fill_manual(values = c('darkturquoise','Blue','forestgreen','Grey'))+
  scale_y_continuous(expand = c(0,0)) +
  theme_classic(base_size=20)+
  theme(axis.title.y = element_blank())
```

##What are the most applicable core business use categories for the web page(s) used by your program(s)?

```{r}
ggplot(dplyr::filter(surveyFunction, acron == 'ODWM'), aes(x = fct_infreq(MainCat)))+
  geom_bar(fill = '#00B1F9')+
  ylab('Count')+
  guides(fill = guide_legend(title = ''))+
  coord_flip()+
  scale_y_continuous(expand = c(0,0)) +
  theme_classic(base_size=20)+
  theme(axis.title.y = element_blank(),plot.margin=unit(c(1,1,1.5,1.2),"cm"))
```

##Who are the target audiences for the web pages used by your program?

```{r}
ggplot(dplyr::filter(audience, acron == 'ODWM'), aes(x = fct_infreq(Audience)))+
  geom_bar(fill = '#00B1F9')+
  ylab('Count')+
  guides(fill = guide_legend(title = ''))+
  coord_flip()+
  scale_y_continuous(expand = c(0,0)) +
  theme_classic(base_size=20)+
  theme(axis.title.y = element_blank(),plot.margin=unit(c(1,1,1.5,1.2),"cm"))
```

##How frequently is content updated from your program(s)?

```{r}
ggplot(dplyr::filter(survey, acron == 'ODWM'), aes(x = sort(ContentUpdate)))+
  geom_bar(fill = '#00B1F9')+
  ylab('Count')+
  xlab('Divisions & Offices')+
  guides(fill = guide_legend(title = ''))+
  scale_y_continuous(expand = c(0,0)) +
  theme_classic(base_size=20)+
  theme(plot.margin=unit(c(1,1,1.5,1.2),"cm"))
```


##Participants

```{r}
ODMMex = dplyr::filter(survey, acron == 'ODWM') %>% dplyr::select(name, programs, WebsiteCreation, ContentTools, website, WebsiteExplanation)
knitr::kable(OIMAex[1])
```

##Describe, in general terms, the process by which your program web pages are developed, updated, and approved for submission to the DIT Web Unit.

```{r}
knitr::kable(ODWMex$WebsiteCreation)
```

##Describe, in general terms, any processes or tools utilized to keep content relevant and current.

```{r}
knitr::kable(ODWMex[4])
```

##Provide a web address of a page from your program that you feel best demonstrates your program’s ability to use the web to meet your business requirements.

```{r}
knitr::kable(ODWMex[5])
```

##Briefly tell us why you selected that web page.
 
```{r}
knitr::kable(ODWMex[6])
```


----

#OIMA

```{r}
OIMA = as.data.frame(splitsurvey[8])
```


##In your program(s), do you use use the web site to publish content, collect content, or both?

```{r}
ggplot(OIMA, aes(x = OIMA.publishORcollectContent))+
  geom_bar(fill = '#8E91FE')+
  xlab('')+
  scale_y_continuous(expand = c(0,0)) +
  theme_classic(base_size=20)+
  ylab('Number of Participants')+
  theme(legend.title = element_blank())
```

##Identify the types and locations of content posted by your program(s). 

```{r}
ggplot(filter(locationsbyweb, acron == 'OIMA'), aes(x = factor(Location, levels = c('Both','State Water Board Home Page','Program Home and Sub-Page(s)','N/A'))))+
  geom_bar(fill = '#8E91FE')+
  ylab('Number of Programs')+
  guides(fill = guide_legend(title = 'Web Page'))+
  coord_flip()+
  scale_fill_manual(values = c('darkturquoise','Blue','forestgreen','Grey'))+
  scale_y_continuous(expand = c(0,0)) +
  theme_classic(base_size=20)+
  theme(axis.title.y = element_blank())
```



```{r}
ggplot(filter(locationsbyweb, acron == 'OIMA'), aes(x = Document, fill = factor(Location, levels = c('Both','State Water Board Home Page','Program Home and Sub-Page(s)','N/A'))))+
  geom_bar()+
  ylab('Number of Participants')+
  guides(fill = guide_legend(title = 'Web Page'))+
  coord_flip()+
  scale_fill_manual(values = c('darkturquoise','Blue','forestgreen','Grey'))+
  scale_y_continuous(expand = c(0,0)) +
  theme_classic(base_size=20)+
  theme(axis.title.y = element_blank())
```

##What are the most applicable core business use categories for the web page(s) used by your program(s)?

```{r}
ggplot(dplyr::filter(surveyFunction, acron == 'OIMA'), aes(x = fct_infreq(MainCat)))+
  geom_bar(fill = '#8E91FE')+
  ylab('Count')+
  guides(fill = guide_legend(title = ''))+
  coord_flip()+
  scale_y_continuous(expand = c(0,0)) +
  theme_classic(base_size=20)+
  theme(axis.title.y = element_blank(),plot.margin=unit(c(1,1,1.5,1.2),"cm"))
```

##Who are the target audiences for the web pages used by your program?

```{r}
ggplot(dplyr::filter(audience, acron == 'OIMA'), aes(x = fct_infreq(Audience)))+
  geom_bar(fill = '#8E91FE')+
  ylab('Count')+
  guides(fill = guide_legend(title = ''))+
  coord_flip()+
  scale_y_continuous(expand = c(0,0)) +
  theme_classic(base_size=20)+
  theme(axis.title.y = element_blank(),plot.margin=unit(c(1,1,1.5,1.2),"cm"))
```

##How frequently is content updated from your program(s)?

```{r}
ggplot(dplyr::filter(survey, acron == 'OIMA'), aes(x = sort(ContentUpdate)))+
  geom_bar(fill = '#8E91FE')+
  ylab('Count')+
  xlab('Divisions & Offices')+
  guides(fill = guide_legend(title = ''))+
  scale_y_continuous(expand = c(0,0)) +
  theme_classic(base_size=20)+
  theme(plot.margin=unit(c(1,1,1.5,1.2),"cm"))
```

##Participants

```{r}
OIMAex = dplyr::filter(survey, acron == 'OIMA') %>% dplyr::select(name, programs, WebsiteCreation, ContentTools, website, WebsiteExplanation)
knitr::kable(OIMAex[1])
```

##Describe, in general terms, the process by which your program web pages are developed, updated, and approved for submission to the DIT Web Unit.

```{r}
knitr::kable(OIMAex$WebsiteCreation)
```

##Describe, in general terms, any processes or tools utilized to keep content relevant and current.

```{r}
knitr::kable(OIMAex[4])
```

##Provide a web address of a page from your program that you feel best demonstrates your program’s ability to use the web to meet your business requirements.

```{r}
knitr::kable(OIMAex[5])
```

##Briefly tell us why you selected that web page.
 
```{r}
knitr::kable(OIMAex[6])
```


----

#OPP

```{r}
OPP = as.data.frame(splitsurvey[9])
```


##In your program(s), do you use use the web site to publish content, collect content, or both?

```{r}
ggplot(OPP, aes(x = OPP.publishORcollectContent))+
  geom_bar(fill = '#EC69F3')+
  xlab('')+
  scale_y_continuous(expand = c(0,0)) +
  theme_classic(base_size=20)+
  ylab('Number of Participants')+
  theme(legend.title = element_blank())
```

##Identify the types and locations of content posted by your program(s). 

```{r}
ggplot(filter(locationsbyweb, acron == 'OPP'), aes(x = factor(Location, levels = c('Both','State Water Board Home Page','Program Home and Sub-Page(s)','N/A'))))+
  geom_bar(fill = '#EC69F3')+
  ylab('Number of Programs')+
  guides(fill = guide_legend(title = 'Web Page'))+
  coord_flip()+
  scale_fill_manual(values = c('darkturquoise','Blue','forestgreen','Grey'))+
  scale_y_continuous(expand = c(0,0)) +
  theme_classic(base_size=20)+
  theme(axis.title.y = element_blank())
```



```{r}
ggplot(filter(locationsbyweb, acron == 'OPP'), aes(x = Document, fill = factor(Location, levels = c('Both','State Water Board Home Page','Program Home and Sub-Page(s)','N/A'))))+
  geom_bar()+
  ylab('Number of Participants')+
  guides(fill = guide_legend(title = 'Web Page'))+
  coord_flip()+
  scale_fill_manual(values = c('darkturquoise','Blue','forestgreen','Grey'))+
  scale_y_continuous(expand = c(0,0)) +
  theme_classic(base_size=20)+
  theme(axis.title.y = element_blank())
```

##What are the most applicable core business use categories for the web page(s) used by your program(s)?

```{r}
ggplot(dplyr::filter(surveyFunction, acron == 'OPP'), aes(x = fct_infreq(MainCat)))+
  geom_bar(fill = '#EC69F3')+
  ylab('Count')+
  guides(fill = guide_legend(title = ''))+
  coord_flip()+
  scale_y_continuous(expand = c(0,0)) +
  theme_classic(base_size=20)+
  theme(axis.title.y = element_blank(),plot.margin=unit(c(1,1,1.5,1.2),"cm"))
```

##Who are the target audiences for the web pages used by your program?

```{r}
ggplot(dplyr::filter(audience, acron == 'OPP'), aes(x = fct_infreq(Audience)))+
  geom_bar(fill = '#EC69F3')+
  ylab('Count')+
  guides(fill = guide_legend(title = ''))+
  coord_flip()+
  scale_y_continuous(expand = c(0,0)) +
  theme_classic(base_size=20)+
  theme(axis.title.y = element_blank(),plot.margin=unit(c(1,1,1.5,1.2),"cm"))
```

##How frequently is content updated from your program(s)?

```{r}
ggplot(dplyr::filter(survey, acron == 'OPP'), aes(x = sort(ContentUpdate)))+
  geom_bar(fill = '#EC69F3')+
  ylab('Count')+
  xlab('Divisions & Offices')+
  guides(fill = guide_legend(title = ''))+
  scale_y_continuous(expand = c(0,0)) +
  theme_classic(base_size=20)+
  theme(plot.margin=unit(c(1,1,1.5,1.2),"cm"))
```

##Participants

```{r}
OPPex = dplyr::filter(survey, acron == 'OPP') %>% dplyr::select(name, programs, WebsiteCreation, ContentTools, website, WebsiteExplanation)
knitr::kable(OPPex[1])
```

##Describe, in general terms, the process by which your program web pages are developed, updated, and approved for submission to the DIT Web Unit.

```{r}
knitr::kable(OPPex$WebsiteCreation)
```

##Describe, in general terms, any processes or tools utilized to keep content relevant and current.

```{r}
knitr::kable(OPPex[4])
```

##Provide a web address of a page from your program that you feel best demonstrates your program’s ability to use the web to meet your business requirements.

```{r}
knitr::kable(OPPex[5])
```

##Briefly tell us why you selected that web page.
 
```{r}
knitr::kable(OPPex[6])
```


#ORPP

```{r}
ORPP = as.data.frame(splitsurvey[10])
```


##In your program(s), do you use use the web site to publish content, collect content, or both?

```{r}
ggplot(ORPP, aes(x = ORPP.publishORcollectContent))+
  geom_bar(fill = '#FF5FC1')+
  xlab('')+
  scale_y_continuous(expand = c(0,0)) +
  theme_classic(base_size=20)+
  ylab('Number of Participants')+
  theme(legend.title = element_blank())
```

##Identify the types and locations of content posted by your program(s). 

```{r}
ggplot(filter(locationsbyweb, acron == 'ORPP'), aes(x = factor(Location, levels = c('Both','State Water Board Home Page','Program Home and Sub-Page(s)','N/A'))))+
  geom_bar(fill = '#FF5FC1')+
  ylab('Number of Programs')+
  guides(fill = guide_legend(title = 'Web Page'))+
  coord_flip()+
  scale_fill_manual(values = c('darkturquoise','Blue','forestgreen','Grey'))+
  scale_y_continuous(expand = c(0,0)) +
  theme_classic(base_size=20)+
  theme(axis.title.y = element_blank())
```



```{r}
ggplot(filter(locationsbyweb, acron == 'ORPP'), aes(x = Document, fill = factor(Location, levels = c('Both','State Water Board Home Page','Program Home and Sub-Page(s)','N/A'))))+
  geom_bar()+
  ylab('Number of Participants')+
  guides(fill = guide_legend(title = 'Web Page'))+
  coord_flip()+
  scale_fill_manual(values = c('darkturquoise','Blue','forestgreen','Grey'))+
  scale_y_continuous(expand = c(0,0)) +
  theme_classic(base_size=20)+
  theme(axis.title.y = element_blank())
```

##What are the most applicable core business use categories for the web page(s) used by your program(s)?

```{r}
ggplot(dplyr::filter(surveyFunction, acron == 'ORPP'), aes(x = fct_infreq(MainCat)))+
  geom_bar(fill = '#FF5FC1')+
  ylab('Count')+
  guides(fill = guide_legend(title = ''))+
  coord_flip()+
  scale_y_continuous(expand = c(0,0)) +
  theme_classic(base_size=20)+
  theme(axis.title.y = element_blank(),plot.margin=unit(c(1,1,1.5,1.2),"cm"))
```

##Who are the target audiences for the web pages used by your program?

```{r}
ggplot(dplyr::filter(audience, acron == 'ORPP'), aes(x = fct_infreq(Audience)))+
  geom_bar(fill = '#FF5FC1')+
  ylab('Count')+
  guides(fill = guide_legend(title = ''))+
  coord_flip()+
  scale_y_continuous(expand = c(0,0)) +
  theme_classic(base_size=20)+
  theme(axis.title.y = element_blank(),plot.margin=unit(c(1,1,1.5,1.2),"cm"))
```

##How frequently is content updated from your program(s)?

```{r}
ggplot(dplyr::filter(survey, acron == 'ORPP'), aes(x = sort(ContentUpdate)))+
  geom_bar(fill = '#FF5FC1')+
  ylab('Count')+
  xlab('Divisions & Offices')+
  guides(fill = guide_legend(title = ''))+
  scale_y_continuous(expand = c(0,0)) +
  theme_classic(base_size=20)+
  theme(plot.margin=unit(c(1,1,1.5,1.2),"cm"))
```

##Participants

```{r}
ORPPex = dplyr::filter(survey, acron == 'ORPP') %>% dplyr::select(name, programs, WebsiteCreation, ContentTools, website, WebsiteExplanation)
knitr::kable(ORPPex[1])
```

##Describe, in general terms, the process by which your program web pages are developed, updated, and approved for submission to the DIT Web Unit.

```{r}
knitr::kable(ORPPex$WebsiteCreation)
```

##Describe, in general terms, any processes or tools utilized to keep content relevant and current.

```{r}
knitr::kable(ORPPex[4])
```

##Provide a web address of a page from your program that you feel best demonstrates your program’s ability to use the web to meet your business requirements.

```{r}
knitr::kable(ORPPex[5])
```

##Briefly tell us why you selected that web page.
 
```{r}
knitr::kable(ORPPex[6])
```

