---
title: "State Water Board Web and Business Requirements Internal Survey"
author: "Nicole Hack"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
  word_document: default
  html_notenook: default
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F)
```

```{r, include = F}
packages <- c('readxl',
              'tidyverse',
              'readr',
              'data.table',
              'dplyr',
              'car',
              'ggplot2',
              'nortest',
              'broom',
              'lme4',
              'magrittr',
              'forcats')
lapply(packages, require, character.only = T)
```

```{r}
survey = read_csv("C:/Users/NHack/Water-board.git/Web Team - Internal Survey (Responses) - Form Responses 1.csv")
survey$publishORcollectContent = as.factor(survey$publishORcollectContent)
levels(survey$publishORcollectContent) = c('Collect Content', 'Publish Content', 'Both')
survey = dplyr::mutate(survey, acron = car::recode(division,"
                                                   'Division of Water Rights'= 'DWR';
                                                   'Division of Drinking Water' = 'DDW';
                                                   'Office of Research, Planning & Performance' = 'ORPP';
                                                   'Division of Administrative Services'= 'DAS';
                                                   'Office of the Delta Water Master' = 'ODWM';
                                                   'Division of Financial Assistance' = 'DFA';
                                                   'Office of Information Management & Analysis'= 'OIMA';
                                                   'EEO' = 'EEO';
                                                   'Office of Public Participation' = 'OPP';
                                                   'Division of Water Quality - Surface Water Regulatory Branch' = 'DWQ-Surf'"))
```





Summary of number of programs who participated in this survey.

```{r}
sumsurvey = survey %>% dplyr::group_by(division, acron) %>%
  dplyr::summarise(NumberOfPrograms = n())
knitr::kable(sumsurvey)
```

##In your program(s), do you use use the web site to publish content, collect content, or both?

```{r}
websiteuse = survey %>% dplyr::group_by(acron) %>% count(publishORcollectContent)
ggplot(websiteuse, aes(x = publishORcollectContent, y = n, fill = acron))+
  geom_bar(stat = 'identity')+
  xlab('')+
  scale_y_continuous(expand = c(0,0)) +
  theme_classic()+
  ylab('Number of Programs')+
  theme(legend.title = element_blank())
```

##Identify the types and locations of content posted by your program(s). 

```{r}
locations = dplyr::select(survey,name,division, acron,programs,contains('Location'))
locationsbyweb = tidyr::gather(locations, 'Document','Location',5:length(locations))
locationsbyweb$Document = gsub('Location','',locationsbyweb$Document)
levels(locationsbyweb$Location) = c('Both','State Water Board Home Page','Program Home and Sub-Page(s)','N/A')
ggplot(locationsbyweb, aes(x = acron, fill = factor(Location, levels = c('Both','State Water Board Home Page','Program Home and Sub-Page(s)','N/A'))))+
  geom_bar()+
  ylab('Number of Programs')+
  guides(fill = guide_legend(title = 'Web Page'))+
  coord_flip()+
  scale_fill_manual(values = c('darkturquoise','Blue','forestgreen','Grey'))+
  scale_y_continuous(expand = c(0,0)) +
  theme_classic()+
  theme(axis.title.y = element_blank())
```



```{r}
ggplot(locationsbyweb, aes(x = Document, fill = factor(Location, levels = c('Both','State Water Board Home Page','Program Home and Sub-Page(s)','N/A'))))+
  geom_bar()+
  ylab('Number of Programs')+
  guides(fill = guide_legend(title = 'Web Page'))+
  coord_flip()+
  scale_fill_manual(values = c('darkturquoise','Blue','forestgreen','Grey'))+
  scale_y_continuous(expand = c(0,0)) +
  theme_classic()+
  theme(axis.title.y = element_blank())
```

##What are the most applicable core business use categories for the web page(s) used by your program(s)?

```{r}
library(splitstackshape)
surveyFunction = cSplit(survey,'Function', ',') %>%
  tidyr::gather('FunNum','MainCat',27:length(.)) %>%
  dplyr::select('name', 'division', 'acron','programs', 'MainCat')
surveyFunction$MainCat = car::recode(surveyFunction$MainCat,"'Announcements' = 'Annoucements';
              'Public Record (Orders' = 'Public Records';
              'Coordination/Organizational Use (Agendas' = 'Coordination/Organizational Use';
              'Achievements/ Work Products' = 'Achievements/ Work Products';
              'Education & Training' = 'Education & Training';
              'Outreach' = 'Outreach';
              'Program Overview/Information' = 'Program Overview/Information';
              'Repository/Library/Collection (of internally and externally developed resources and links)' = 'Repository';
              else = NA")
surveyFunction = surveyFunction[complete.cases(surveyFunction),]

ggplot(surveyFunction, aes(fill = acron, x = fct_infreq(MainCat)))+
  geom_bar()+
  ylab('Number of Programs')+
  guides(fill = guide_legend(title = ''))+
  coord_flip()+
  scale_y_continuous(expand = c(0,0)) +
  theme_classic()+
  theme(axis.title.y = element_blank(),plot.margin=unit(c(1,1,1.5,1.2),"cm"))
```

##Who are the target audiences for the web pages used by your program?

```{r}
audience = survey %>% cSplit('audience', ',') %>%
  tidyr::gather('Trash','Audience',27:length(.)) %>%
  dplyr::select('name', 'division','acron', 'programs', 'Audience')
audience$Audience = car::recode(audience$Audience,"
'Internal Staff' = 'Internal Staff';
'Private Industry (Ag' = 'Private Industry';
'Non-Government Organizations (NGOs)' = 'Non-Government Organizations (NGOs)';
'General Public' = 'General Public';
'Businesses' = 'Businesses';
'Municipalities' = 'Municipalities';
'Management' = 'Management';
'Other Agencies' = 'Other Agencies';
'Tribes' = 'Tribes';
'Citizen Scientists' = 'Citizen Scientists';
'Certified operators' = 'Certified operators';
'Retail and wholesale water suppliers throughout the state with an emphasis on 410 urban water suppliers.' = 'Water suppliers';
else = NA")
audience = audience[complete.cases(audience),]

ggplot(audience, aes(fill = acron, x = fct_infreq(Audience)))+
  geom_bar()+
  ylab('Number of Programs')+
  guides(fill = guide_legend(title = ''))+
  coord_flip()+
  scale_y_continuous(expand = c(0,0)) +
  theme_classic()+
  theme(axis.title.y = element_blank(),plot.margin=unit(c(1,1,1.5,1.2),"cm"))
```

##Identify the number of staff utilized to keep content relevant and current. 

```{r}
sumstaff = survey %>% dplyr::group_by(acron) %>% dplyr::summarise(staffnum = sum(ceiling(Staffnum)),webhrs = sum(ceiling(hoursnum)))
sumstaff$acron = reorder(sumstaff$acron, sumstaff$staffnum)
ggplot(sumstaff, aes(x = acron, y = staffnum))+
  geom_bar(stat = 'identity', color = 'black', fill = 'Blue')+
  ylab('Number of staff')+
  xlab('Divisions & Offices')+
  guides(fill = guide_legend(title = ''))+
  scale_y_continuous(expand = c(0,0)) +
  theme_classic()+
  theme(plot.margin=unit(c(1,1,1.5,1.2),"cm"))
```

##Identify the approximate amount of hours expended each month to keep content relevant and current.

```{r}
ggplot(sumstaff, aes(x = reorder(acron, webhrs), y = webhrs))+
  geom_bar(stat = 'identity', color = 'black', fill = 'Blue')+
  ylab('Number of hr/mo')+
  xlab('Divisions & Offices')+
  guides(fill = guide_legend(title = ''))+
  scale_y_continuous(expand = c(0,0)) +
  theme_classic()+
  theme(plot.margin=unit(c(1,1,1.5,1.2),"cm"))

ggplot(sumstaff, aes(x = staffnum, y = webhrs, color = acron))+
  geom_point()+
  xlab('Number of Staff')+
  ylab('Number of hr/mo')+
  guides(color = guide_legend(title = ''))+
  theme_classic()+
  theme(plot.margin=unit(c(1,1,1.5,1.2),"cm"))
```

* For comparison, an employee working 24 hr/mo works about 5.5 hr/wk


##How frequently is content updated from your program(s)?

```{r}
update = survey %>% dplyr::group_by(acron) %>% count(ContentUpdate) 
update$ContentUpdate = as.factor(update$ContentUpdate)
levels(update$ContentUpdate) = c('Yearly','Quarterly','Monthly','Weekly','Daily','Hourly')
ggplot(update, aes(x = ContentUpdate, y = n, fill = acron))+
  geom_bar(stat = 'identity')+
  ylab('Number of programs')+
  xlab('Divisions & Offices')+
  guides(fill = guide_legend(title = ''))+
  scale_y_continuous(expand = c(0,0)) +
  theme_classic()+
  theme(plot.margin=unit(c(1,1,1.5,1.2),"cm"))
```